%-------------------------
% Resume — Thejaswini Thatigutla
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section heading: minimal space above, tight below
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule\vspace{2pt}]

\pdfgentounicode=1

%--- Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1}\vspace{1pt}}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \small#3 & \small\textit{#4} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{2pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, topsep=0pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=2pt, itemsep=1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Thejaswini Thatigutla} \\ \vspace{10pt}
    \small
    \faEnvelope\kern3pt
    \href{mailto:thejaswini.t9920@gmail.com}{\underline{thejaswini.t9920@gmail.com}}
    \kern10pt\textbar\kern10pt
    \faLinkedin\kern3pt LinkedIn
    \kern10pt\textbar\kern10pt
    \faGithub\kern3pt
    \href{https://github.com/tthejaswini}{\underline{tthejaswini}}
    \kern10pt\textbar\kern10pt
    \small\faCode\kern3pt LeetCode
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Indian Institute of Information Technology, Gwalior}{Gwalior, India}
      {\textbf{B.Tech in Information Technology}}{2024 -- Present}
      \resumeItemListStart
        \resumeItem{CGPA: \textbf{8.45}}
        \resumeItem{Coursework: Data Structures \& Algorithms, Design \& Analysis of Algorithms, Object-Oriented Programming, Operating Systems, Database Management Systems, Computer Networks, Digital Logic Design, Discrete Mathematics}
      \resumeItemListEnd

    \resumeSubheading
      {Indian Institute of Technology Madras}{Online}
      {Foundational Certificate in Data Science and Programming}{2024 -- 2025}

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon}{Bangalore, India}
      {Software Development Engineer Intern — EPIC Team}{May 2026 -- July 2026}
      \resumeItemListStart
        \resumeItem{Built \textbf{CloudWatch monitoring dashboards} for the EPIC team to visualize production metrics and system health in real time.}
        \resumeItem{Configured \textbf{CloudWatch alarms} and metric filters to proactively detect production anomalies and trigger automated alerts.}
        \resumeItem{Worked with \textbf{AWS services} — S3, EventBridge, API Gateway, Lambda, SQS, SNS — and developed backend components in \textbf{Java, JavaScript, and TypeScript}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Skill Swap Platform} $|$ \emph{React, Node.js, Express.js, MongoDB, REST APIs}}{2025}
        \resumeItemListStart
          \resumeItem{Built a full-stack peer-to-peer skill exchange platform with secure authentication and user-matching logic.}
          \resumeItem{Designed RESTful APIs for seamless frontend-backend integration; built a responsive UI across devices.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}, topsep=0pt, partopsep=0pt, itemsep=3pt]
    \small\item{
      \begin{tabular}[t]{@{}l@{\hskip 10pt}l}
        \textbf{Languages}         & C, C++, Java, Python, JavaScript, TypeScript, SQL, Verilog \\[2pt]
        \textbf{Web \& Frameworks} & HTML, CSS, React, Node.js, Express.js \\[2pt]
        \textbf{AWS / Cloud}       & CloudWatch, S3, EventBridge, API Gateway, Lambda, SQS, SNS \\[2pt]
        \textbf{Databases}         & MySQL, MongoDB \\[2pt]
        \textbf{Tools}             & Git, GitHub, VS Code, Postman, Quip \\[2pt]
      \end{tabular}
    }
  \end{itemize}\vspace{-6pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Activities}
  \begin{itemize}[leftmargin=0.2in, label=\small$\bullet$, topsep=0pt, partopsep=0pt, itemsep=3pt, parsep=0pt]
    \small\item \textbf{Flipkart Girls Wanna Code (GWC) 7.0} \textit{(2025)} — Selected among the \textbf{top 200 from 25,000+} applicants nationwide in Flipkart's flagship coding program for women in tech.

    \small\item \textbf{Executive Member, Student Gyan Movement} — IIIT Gwalior: Organized and managed academic support initiatives for students across the institute.

    \small\item \textbf{Executive Member, Student Activity Council (Welfare)} — IIIT Gwalior: Contributed to student welfare programs and coordinated institute-level events.

    \small\item \textbf{Organizer, Ideathon – Infostav Tech Fest} — IIIT Gwalior: Planned and executed the ideation event; handled coordination, participant management, and on-ground execution.

    \small\item \textbf{Alumni Meet '26 Representative} — IIIT Gwalior: Coordinated alumni interaction, event logistics, and session management.
  \end{itemize}

\end{document}
